Learning to communicate using recursive pragmatic reasoning about other agents

### 2013-05-31 praglearn.tex
author initials

\author{
Nathaniel Smith\thanks{...} \\
School of Informatics\\
University of Edinburgh\\
Edinburgh, Scotland, UK\\
\texttt{nathaniel.smith@ed.ac.uk} \\
\AND
Noah D. Goodman \\
Department of Psychology\\
Stanford University \\
Stanford, CA, USA \\
\texttt{ngoodman@stanford.edu} \\
\And
Michael C. Frank \\
Department of Psychology \\
Stanford University \\
Stanford, CA, USA \\
\texttt{mcfrank@stanford.edu}}

>>>>

\author{
Nathaniel J.~Smith\thanks{...} \\
School of Informatics\\
University of Edinburgh\\
Edinburgh, Scotland, UK\\
\texttt{nathaniel.smith@ed.ac.uk} \\
\AND
Noah D.~Goodman \\
Department of Psychology\\
Stanford University \\
Stanford, CA, USA \\
\texttt{ngoodman@stanford.edu} \\
\And
Michael C.~Frank \\
Department of Psychology \\
Stanford University \\
Stanford, CA, USA \\
\texttt{mcfrank@stanford.edu}}
